\documentclass{article}
\usepackage[a4paper, left=0.9in, right=0.9in, top=15mm, bottom=6mm]{geometry}
\usepackage{fontawesome}
\usepackage{changepage}
\usepackage{booktabs}
\usepackage{dashrule}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{ragged2e}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{titling}
\usepackage{lipsum}
\usepackage{xcolor}
\newcommand{\yourlight}[1]{\textcolor{gray}{#1}}
\newcommand{\youremail}[1]{\href{mailto:#1}{#1}}
\newcommand{\yoursocial}[2]{{\Large #1}\hspace{0.5em}\yourlight{\href{https://#2}{#2}}}\newcommand{\yourjustify}[1]{\makebox[	extwidth][s]{#1}}
\newcommand{\yourtitle}[4]{
  \begin{center}
    {\huge\bfseries #1}\\
    \vspace{0.5em}
    \youremail{#3}\\
    {#2}\\
  \end{center}
}
\newcommand{\yourfooter}[1]{
  \vfill
  \begin{center}
    #1
  \end{center}
}
\newcommand{\yourmiddle}[1]{\noindent\parbox[c]{\hsize}{#1}}
\titleformat{\section}{\LARGE\bfseries}{}{1em}{}[\titlerule]
\titlespacing{\section}{0em}{1.4em}{0.7em}
\titlespacing{\subsection}{0em}{0.5em}{-0.2em}
\newcolumntype{b}{X}
\newcolumntype{s}{>{\hsize=.5\hsize}X}
\setlength{\columnseprule}{0.4pt}
\setlength\multicolsep{0pt}
\linespread{0.9}
\setlist{nosep}
\pagenumbering{gobble}
\hypersetup{colorlinks, linkcolor={red!50!black}, citecolor={blue!50!black}, urlcolor={blue!70!black}}
\begin{document}
\yourtitle{Brandon Ibbotson}{Ballymena, Co. Antrim}{brandon.ibbotson2@mail.dcu.ie}{byxor.xyz}
\section{Overview}
\begin{tabularx}{\textwidth}{ll}
\vspace{0.75em}
\textbf{Skills} & Test-Driven Development, {} Agile, {} Git\\
\vspace{0.75em}
\textbf{Primary Languages} & Go, {} Python, {} Kotlin, {} JavaScript (ES6/ES7), {} Java, {} C, {} C++\\
\textbf{Extra Languages} & Haskell, {} Intel x86/x64, {} LIMP, {} C\#, {} UnityScript, {} Ruby, {} Clojure, {} Prolog\\
\end{tabularx}
\section{Experience}
\subsection{Arista Networks (Dublin) - Software Engineering Intern}
\textit{June 2017 - June 2018}

Wrote/Tested/Deployed TACC \& C++ on high-performance switches around the world. Maintained Arista EOS Operating System. Worked exclusively in CLI over SSH. Interacted with switch hardware to toggle various features.

\textit{\textbf{Technologies}: TACC, C++, C, Perforce}
\vspace{0.5em}
\subsection{Instil Software (Belfast) - Software Engineering Intern}
\textit{July 2016 - September 2016}

Full Stack Developer. Built REST API \& Email Service with Kotlin. Increased test coverage by \textasciitilde{}15\% in first month. Maintained AngularJS frontend. Received first-class training on TDD and Refactoring.

\textit{\textbf{Technologies}: Kotlin, AngularJS, DropWizard, PostgreSQL, Swagger}
\vspace{0.5em}
\section{Projects}
\vspace{1em}
\begin{multicols}{2}
\parbox{\linewidth}{\textbf{LIMP} - Functional Programming Language with 99\% Test Coverage. Interpreter supports anonymous functions, objects, collections, strings, recursion, immutability, scoped constants, and a small standard library. Comes with a REPL. (\href{http://www.github.com/byxor/limp}{github})\\
\textit{\textbf{Technologies}: Python3.6}}\vspace{1.5em}\\\parbox{\linewidth}{\textbf{Entua} - Android/iOS IoT app to configure events on smart devices within the Home. React-Native frontend. Go WebSocket backend. Raspberry Pi Hub. (proprietary, no source)\\
\textit{\textbf{Technologies}: Go, ES6, React-Native, Redux}}\vspace{1.5em}\\\parbox{\linewidth}{\textbf{byxor.xyz} - Personal website. Hosts my programming blog and small interactive demos. (\href{http://www.github.com/byxor/website}{github})\\
\textit{\textbf{Technologies}: Angular 5, TypeScript}}\vspace{1.5em}\\\parbox{\linewidth}{\textbf{Passflip} - A lightweight SHA224-based password manager. Installable via pip. (\href{http://www.github.com/byxor/passflip}{github})\\
\textit{\textbf{Technologies}: Python}}\vspace{1.5em}\\\parbox{\linewidth}{\textbf{Slimput} - Faster input scanners for Java. (\href{http://www.github.com/byxor/slimput}{github})\\
\textit{\textbf{Technologies}: Java}}\vspace{1.5em}\\\parbox{\linewidth}{\textbf{Kapoki} - A multi-language skeleton generator for new projects. (\href{http://www.github.com/byxor/kapoki}{github})\\
\textit{\textbf{Technologies}: Bash, C++, Python}}
\end{multicols}
\begin{center}
\vspace{1em}
See more projects at \url{byxor.xyz/projects}
\end{center}
\section{Education}
{\large\textbf{Dublin City University, Ireland}}: \textit{September 2015 - June 2019}

\textbf{BSc. Computational Problem Solving \& Software Development}

{Find out more at \url{www.cpssd.net}}
\yourfooter{
\vspace{1em}
\begin{tabularx}{\linewidth}{*3{>{\Centering}X}}
\yoursocial{\faGithub}{github.com/byxor} & \yoursocial{\faStackOverflow}{stackoverflow.com/users/5601284} & \yoursocial{\faLaptop}{byxor.xyz}\\
\end{tabularx}

This CV was rendered with \textbf{Python} {\&} \textbf{{\LaTeX}} (\url{https://www.github.com/byxor/cv}).\\
}
\end{document}